---
title: "Brand Analysis"
author: "Jonas Gehrlein"
date: "11/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
df <-read.csv("~/Documents/Projects/brand_analysis/filtered.csv")
normalization <- 1/10000000000

# Some accounts have no Balance because they had no balance at the snapshot and their voting power is 0
df$Balance <- ifelse(is.na(df$Balance),0, df$Balance)

df$Identity.A <- df$Identity.A / 100
df$Identity.B <- df$Identity.B / 100

df$Logo.A <- df$Logo.A / 100
df$Logo.B <- df$Logo.B / 100


# Normalize to DOTs
df$Balance <- df$Balance*normalization

# Take square root of balance to account for quadratic voting
df$sqrt_balance <- sqrt(df$Balance)
```

```{r, echo=FALSE}
# Weigh the square root balances (voting power) with the assigned voting weight.
df$result_identity_A <- df$sqrt_balance * df$Identity.A
df$result_identity_B <- df$sqrt_balance * df$Identity.B

df$result_logo_A <- df$sqrt_balance * df$Logo.A
df$result_logo_B <- df$sqrt_balance * df$Logo.B


# Sum the square root balances that support the different campaigns.
sum_identity_A <- sum(df$result_identity_A)
sum_identity_B <- sum(df$result_identity_B)

identity_B_share <- sum_identity_B / (sum_identity_A + sum_identity_B)
identity_A_share <- sum_identity_A / (sum_identity_A + sum_identity_B)

sum_logo_A <- sum(df$result_logo_A)
sum_logo_B <- sum(df$result_logo_B)

logo_B_share <- sum_logo_B / (sum_logo_A + sum_logo_B)
logo_A_share <- sum_logo_A / (sum_logo_A + sum_logo_B)


```

```{r, echo=FALSE}
identity_certain <- nrow(subset(df, Identity.A == 1 | df$Identity.A == 0))
identity_tendency <- nrow(subset(df, Identity.A == 0.25 | Identity.A == 0.75))
identity_uncertain <- nrow(subset(df, Identity.A == 0.5))


logo_certain <- nrow(subset(df, Logo.A == 1 | df$Logo.A == 0))
logo_tendency <- nrow(subset(df, Logo.A == 0.25 | Logo.A == 0.75))
logo_uncertain <- nrow(subset(df, Logo.A == 0.5))

```


# Results

## Voting results

A total sum of `r (format(sum(df$Balance), scientific=FALSE, big.mark=","))` DOT has been used during the voting process by `r nrow(df)` accounts. Due to the quadratic voting mechanism, the overall voting power equals `r (format(sum(df$sqrt_balance), scientific=FALSE, big.mark=","))` VP. 


|          | A              | B              |
|----------|----------------|----------------|
| Identity |  `r format(sum_identity_A, scientific=FALSE, big.mark=",")` VP  (`r format(identity_A_share*100,digits=2)`%)            |    `r format(sum_identity_B, scientific=FALSE, big.mark=",")` VP  (`r format(identity_B_share*100, digits=2)`%)           |
| Logo     | `r format(sum_logo_A, scientific=FALSE, big.mark=",")` VP (`r format(logo_A_share*100,digits=2)`%) | `r format(sum_logo_B, scientific=FALSE, big.mark=",")` VP (`r format(logo_B_share*100,digits=2)`%)  |

The table shows the weighted square root balances that support the two different identities and logos, which can be considered as Voting Power (VP). 

## Certainty

The following table shows how many voters selected the different weight options available. A vote with a weight of 100% (in any direction) is counted as a *Strong* opinion. A vote of 75% (in any direction) is counted as *Medium* opinion and a vote with weights of 50% is considered an *Indifferent* opinion.

| Category / Opinion         | Strong | Medium | Indifferent |
|----------|---------|----------|-----------|
| Identity | `r identity_certain`        |  `r identity_tendency`        |  `r identity_uncertain`         |
| Logo     | `r logo_certain`        |  `r logo_tendency`        |   `r logo_uncertain`        |

